Revisiting Multi-Domain Machine Translation

### 2020-04-22 2020/coling2020/multidomain.tex
TACL style

\documentclass[11pt]{article}
\usepackage{coling2020}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[draft]{todo}
\usepackage{xspace}
\usepackage{amsmath,amsfonts,amssymb}
%\setlength\titlebox{5cm}
%\colingfinalcopy % Uncomment this line for the final submission

@@

%
% The following footnote without marker is needed for the camera-ready
% version of the paper.
% Comment out the instructions (first text) and uncomment the 8 lines
% under "final paper" for your variant of English.
% 
\blfootnote{
    %
    % for review submission
    %
    \hspace{-0.65cm}  % space normally used by the marker
    Place licence statement here for the camera-ready version. See
    Section~\ref{licence} of the instructions for preparing a
    manuscript.
    %
    % % final paper: en-uk version 
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International Licence.
    % Licence details:
    % \url{http://creativecommons.org/licenses/by/4.0/}.
    % 
    % % final paper: en-us version 
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International License.
    % License details:
    % \url{http://creativecommons.org/licenses/by/4.0/}.
}

@@

In this paper, we try to spell out in a more precise fashion the requirements that an effective MDMT system should meet (section~\ref{sec:requirements}). Our first contribution is thus of methodological nature and consists of lists of expected properties of MDMT system and associated measurements to evaluate them (section~\ref{sec:challenging}). In doing so, we also shed lights on new problems that arise in this context, regarding for instance the accomodation of new domains in the course of training, or the computation of automating domain tags.\fyDone{New problems - continuous learning, automatic domains} Our second main contribution is experimental and consists in a thorough reanalysis of eight recent multi-domain approaches from the literature, including a variant of a model initially introduced for DA. We show in section~\ref{sec:experiments}  existing approaches still fall short to match many of these requirements, notably with respect to handling a large amount of heterogeneous domains and to dynamically integrating new domains in training.\fyDone{Spell out conclusions}

\section{Requirements of multi-domain MT \label{sec:requirements}}
In this section, we try to recap the main reasons for considering a multi-domain scenario and discuss their implications in terms of performance evaluation.
\fyDone{Relation to theory, discussion of worst case scenario}
\fyDone{Insist on the work of Dredze}

@@

We conventionally define a domain $d$ as a distribution $\mathcal{D}_d(x)$ over some feature space $\mathcal{X}$ that is shared across domains \cite{Pan10asurvey}: in machine translation, $\mathcal{X}$ is the representation space for source sentences; each domain corresponds to a specific source of data, and differs from the other data sources in terms of textual genre, thematic content \cite{Chen16guided,Zhang16topicinformed}, register \cite{Sennrich16politeness}, style \cite{Niu18multitask}, etc. Translation in domain $d$ is formalized by a translation function $h_d(y|x)$ pairing sentences in a source language with sentences in a target language $y \in \mathcal{Y}$. $h_d$ is usually assumed to be deterministic (hence $y = h_d(x)$, but can differ from one domain to the other.

@@

This definition seems to be the most accepted view of a multi-domain MT\footnote{One important exception is \cite{Farajian17multidomain}, where test translations rely on a similarity scores between test and train sentences, rather than on domain labels.} and one that we also adopt here. Note that in the absence of further specification, the naive answer to the MD setting should be to estimate one translation function $\hat{h}_d(x)$ separately for each domain, then to translate using $\hat{h}(x,d) = \sum_{d'} h_{d'}(x) \indic{d' = d}$, where $\indic{x}$ is the indicator function. We now discuss the arguments that are usually put forward to proceed differently.
% --

@@

% include your own bib file like this:
\bibliographystyle{coling}
\bibliography{multidomain}

>>>>

\documentclass[11pt,a4paper]{article}
% \usepackage{coling2020}
\usepackage{tacl2018v2}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[draft]{todo}
\usepackage{xspace}
\usepackage{amsmath,amsfonts,amssymb}
%\setlength\titlebox{5cm}
%\colingfinalcopy % Uncomment this line for the final submission

@@

%
% The following footnote without marker is needed for the camera-ready
% version of the paper.
% Comment out the instructions (first text) and uncomment the 8 lines
% under "final paper" for your variant of English.
% 
\footnote{
    %
    % for review submission
    %
    \hspace{-0.65cm}  % space normally used by the marker
    Place licence statement here for the camera-ready version. See
    Section~\ref{licence} of the instructions for preparing a
    manuscript.
    %
    % % final paper: en-uk version 
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International Licence.
    % Licence details:
    % \url{http://creativecommons.org/licenses/by/4.0/}.
    % 
    % % final paper: en-us version 
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International License.
    % License details:
    % \url{http://creativecommons.org/licenses/by/4.0/}.
}

@@

In this paper, we spell out in a more precise fashion the requirements that an effective MDMT system should meet (section~\ref{sec:requirements}). Our first contribution is thus of methodological nature and consists of lists of expected properties of MDMT system and associated measurements to evaluate them (section~\ref{sec:challenging}). In doing so, we also shed lights on new problems that arise in this context, regarding for instance the accomodation of new domains in the course of training, or the computation of automating domain tags.\fyDone{New problems - continuous learning, automatic domains} Our second main contribution is experimental and consists in a thorough reanalysis of eight recent multi-domain approaches from the literature, including a variant of a model initially introduced for DA. We show in section~\ref{sec:experiments}  existing approaches still fall short to match many of these requirements, notably with respect to handling a large amount of heterogeneous domains and to dynamically integrating new domains in training.\fyDone{Spell out conclusions}

\section{Requirements of multi-domain MT \label{sec:requirements}}
In this section, we recap the main reasons for considering a multi-domain scenario and discuss their implications in terms of performance evaluation.
\fyDone{Relation to theory, discussion of worst case scenario}
\fyDone{Insist on the work of Dredze}

@@

We conventionally define a domain $d$ as a distribution $\mathcal{D}_d(x)$ over some feature space $\mathcal{X}$ that is shared across domains \cite{Pan10asurvey}: in machine translation, $\mathcal{X}$ is the representation space for source sentences; each domain corresponds to a specific source of data, and differs from the other data sources in terms of textual genre, thematic content \cite{Chen16guided,Zhang16topicinformed}, register \cite{Sennrich16politeness}, style \cite{Niu18multitask}, etc. Translation in domain $d$ is formalized by a translation function $h_d(y|x)$ pairing sentences in a source language with sentences in a target language $y \in \mathcal{Y}$. $h_d$ is usually assumed to be deterministic (hence $y = h_d(x)$), but can differ from one domain to the other.

@@

This definition seems to be the most accepted view of a multi-domain MT\footnote{One important exception is \cite{Farajian17multidomain}, where test translations rely on a similarity scores between test and train sentences, rather than on domain labels.} and one that we also adopt here. Note that in the absence of further specification, the naive answer to the MD setting should be to estimate one translation function $\hat{h}_d(x)$ separately for each domain, then to translate using $\hat{h}(x,d) = \sum_{d'} h_{d'}(x) \indic{d' = d}$, where $\indic{x}$ is the indicator function. We now discuss the arguments that are put forward to proceed differently.
% --

@@

% include your own bib file like this:
% \bibliographystyle{coling}
\bibliographystyle{acl_natbib}
\bibliography{multidomain}
